Arbeidskrav våren 2022

### 2022-01-13 Data/Data_Henting_Backup.Rmd
Skal vera bra

```{r writing_csv}
#oppgave1
write_csv(syssel_arb, file="syssel_arb.csv")
write_csv(hld_arb, file="hld_arb.csv")
write_csv(sun_arb, file="sun_arb.csv")
write_csv(har_arb, file="har_arb.csv")
write_csv(syssel_bos, file="syssel_bos.csv")
write_csv(hld_bos, file="hld_bos.csv")
write_csv(sun_bos, file="sun_bos.csv")
write_csv(har_bos, file="har_bos.csv")
#oppgave 2
write_csv(hld_bos_LQ, file="hld_bos_LQ.csv")
#oppgave 3
#oppgave 4
write_csv(Pendling, file = "Pendling.csv")
write_csv(hgl_Pendling, file = "hgl_Pendling.csv")
write_csv(sun_Pendling, file = "sun_Pendling.csv")
```

>>>>

```{r writing_csv}
#oppgave1
write_csv(syssel_arb, file="syssel_arb.csv")
write_csv(hld_arb, file="hld_arb.csv")
write_csv(sun_arb, file="sun_arb.csv")
write_csv(har_arb, file="har_arb.csv")
write_csv(syssel_bos, file="syssel_bos.csv")
write_csv(hld_bos, file="hld_bos.csv")
write_csv(sun_bos, file="sun_bos.csv")
write_csv(har_bos, file="har_bos.csv")
#oppgave 2

#oppgave 3
write_csv(hld_bos_LQ, file="hld_bos_LQ.csv")
write_csv(sun_bos_LQ, file= "sun_bos_LQ.csv")
#oppgave 4
write_csv(Pendling, file = "Pendling.csv")
write_csv(hgl_Pendling, file = "hgl_Pendling.csv")
write_csv(sun_Pendling, file = "sun_Pendling.csv")
```

### 2022-01-13 MSB106_Arbeidskrav_V22_Backup.Rmd
Skal vera bra

```{r csv_filer}
syssel_arb <- read_csv("Data/syssel_arb.csv", show_col_types = FALSE)
hld_arb <- read_csv("Data/hld_arb.csv", show_col_types = FALSE)
sun_arb <- read_csv("Data/sun_arb.csv", show_col_types = FALSE)
har_arb <- read_csv("Data/har_arb.csv", show_col_types = FALSE)
syssel_bos <- read_csv("Data/syssel_bos.csv", show_col_types = FALSE)
hld_bos <- read_csv("Data/hld_bos.csv", show_col_types = FALSE)
sun_bos <- read_csv("Data/sun_bos.csv", show_col_types = FALSE)
har_bos <- read_csv("Data/har_bos.csv", show_col_types = FALSE)
Pendling <- read_csv("Data/Pendling.csv", show_col_types = FALSE)
hgl_Pendling <- read_csv("Data/hgl_Pendling.csv", show_col_types = FALSE)
sun_Pendling <- read_csv("Data/sun_Pendling.csv", show_col_types = FALSE)
hld_bos_LQ <- read_csv("Data/hld_bos_LQ.csv", show_col_types = FALSE)
```

>>>>

```{r csv_filer}
syssel_arb <- read_csv("Data/syssel_arb.csv", show_col_types = FALSE)
hld_arb <- read_csv("Data/hld_arb.csv", show_col_types = FALSE)
sun_arb <- read_csv("Data/sun_arb.csv", show_col_types = FALSE)
har_arb <- read_csv("Data/har_arb.csv", show_col_types = FALSE)
syssel_bos <- read_csv("Data/syssel_bos.csv", show_col_types = FALSE)
hld_bos <- read_csv("Data/hld_bos.csv", show_col_types = FALSE)
sun_bos <- read_csv("Data/sun_bos.csv", show_col_types = FALSE)
har_bos <- read_csv("Data/har_bos.csv", show_col_types = FALSE)
Pendling <- read_csv("Data/Pendling.csv", show_col_types = FALSE)
hgl_Pendling <- read_csv("Data/hgl_Pendling.csv", show_col_types = FALSE)
sun_Pendling <- read_csv("Data/sun_Pendling.csv", show_col_types = FALSE)
hld_bos_LQ <- read_csv("Data/hld_bos_LQ.csv", show_col_types = FALSE)
sun_bos_LQ <- read_csv("Data/sun_bos_LQ.csv", show_col_types = FALSE)
```
